---
title: "TITANIC DATASET"
author: "Preethika P"
date: "2 November 2019"
output: html_document
---
##clean train data
```{r}
a<-read.csv(file.choose())
summary(a)
```



##replace missing values
```{r}
a$Age<- ifelse(is.na(a$Age), median(a$Age, na.rm=TRUE), a$Age)

```


##drop the column with categorical missing value and also unwanted column like name
```{r}
library(dplyr)
a<-select (a,-c(Cabin,Name,Ticket))

```


##create dummy variable
```{r}
library(dummies)
b=dummy(a$Sex, sep = ".")
c<-dummy(a$Embarked,sep=".")
e<-a[,-c(4,9)] ##remove the categorical -dummy variable like sex and embarked
d<-data.frame(e,b,c)
f<-d[,-c(8,10,11)] ##removed the each one column from each dummy variable

library(car)
vif(lm(Survived~.,data=f))

```



##save the clean train data in r
```{r}
write.csv(f,"t_train.csv")
```



## clean test data
```{r}
g<-read.csv(file.choose())
summary(g)
g$Age<- ifelse(is.na(g$Age), median(g$Age, na.rm=TRUE), g$Age)
g$Fare<- ifelse(is.na(g$Fare), median(g$Fare, na.rm=TRUE), g$Fare)

```



##drop the column with categorical missing value and also unwanted column like name
```{r}
library(dplyr)
g<-select (g,-c(Cabin,Name,Ticket))

```


##create dummy variable
```{r}
library(dummies)
b=dummy(g$Sex, sep = ".")
c<-dummy(g$Embarked,sep=".")
e<-g[,-c(3,8)] ##remove the categorical -dummy variable like sex and embarked
d<-data.frame(e,b,c)
f<-d[,-c(7,9)] ##removed the each one column from each dummy variable

```



##save the clean train data in r
```{r}
write.csv(f,"t_test.csv")
```




##build model using test and train data
```{r}
train<-read.csv(file.choose())
test<-read.csv(file.choose())
summary(train)
```




##scalling the test and train data
```{r}
train[-3] = scale(train[-3])
test = scale(test)

```



##converting the train and test into data frame 
```{r}
test=data.frame(test)
train<-data.frame(train)
```



##logistic regression
```{r}
classifier = glm(formula = Survived ~ .,
                 family = binomial,
                 data = train)
```


##predict y
```{r}
prob_pred = predict(classifier, test)
y_pred = ifelse(prob_pred > 0.5, 1, 0)
```



##convert the y predict to csv file
```{r}
write.csv(y_pred,"y_pred.csv")
```

##naive bayes
```{r}
library(e1071)
classifier = naiveBayes(x = train[-3],
                        y = train$Survived)

```

##predict y
```{r}
y_pred = predict(classifier, newdata = test)

```

##convert the y predict to csv file
```{r}
write.csv(y_pred,"y_pred_NB.csv")

```

##Random forest
```{r}
library(randomForest)
set.seed(123)
classifier = randomForest(x = train[-3],
                          y = train$Survived,
                          ntree = 500)
```

# Predicting the Test set results
```{r}
prob_pred = predict(classifier, newdata = test)

```

##predicted y
```{r}
y_pred = ifelse(prob_pred > 0.5, 1, 0)

```

##convert the y predict to csv file
```{r}
write.csv(y_pred,"y_pred_RF.csv")

```











